---
title: "Explaining the package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Explaining the package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753SPOT24)
```

# Introduction

This package contains a collection of functions and data used for MATH 4753. It does not contain all of the functions and all of the data, but it does contain those that I found most useful or interesting.

# mybin()

The mybin() function is a binomial simulation, creating a frequency distribution for the simulation.

```{r}
mybin(iter=10000, n=20, p=0.5)
```

# myboot2()

The myboot2() function is a bootstrapping function. It takes a data set and creates a bootstrap estimate of a specified parameter.

```{r}
x = rnorm(20, mean=10, sd=2)
myboot2(iter=10000, x, fun="mean")
```

# mycltu()

The mycltu() function demonstrates the Central Limit Theorem for the sample mean of a uniform distribution.

```{r}
mycltu(n=15, iter=1000, a=1, b=20)
```

# mymlnorm()

The mymlnorm() function finds finds a maximum likelihood estimate for the mean and standard deviation of a normal distribution.

```{r}
x = rnorm(n=30, mean=50, sd=7)
mymlnorm(x=x, mu=1:100, sig=1:10)
```

# myncurve()

The myncurve() function gives a graphical representation of P(X < a) for a normal distribution, as well as the probability.

```{r}
myncurve(mu=20, sigma=2, a=18)
```

# ntickets()

The ntickets() function was created for Project 1, which deals with the problem of overbooking plane flights. It considers the number of seats on a plane, the expected probability of someone with a ticket showing up to take a seat, and the desired probability of overbooking, and finds the greatest number of tickets that can be sold without exceeding the desired probability of overbooking, using a binomial distribution and the normal approximation to the binomial distribution.

```{r}
ntickets(N=300, gamma=0.01, p=0.95)
```


